---
title: "Check transfer completeness in the qPortal"
output: html_notebook
author: "Andrea Borbon-Garcia"
date: "2025-10-29"
---

```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # Print code chunks
```

```{r}
source("notebooks/checkup_transfer_function.R") # Load the function 
```


```{r}
#Tests with different inputs
# Change working directory to the notebook location

qportal_report_filepath = "../test_data/251112_NCCT_VOOLSTRA_Q2181_Raw_Data_duplicates.tsv"
    
demultiplexed_files_filepath = "test_data/demultiplexed_files.txt"

#Test with with demultiplexed files filepath
checkup_transfer(qportal_report_filepath,
                  demultiplexed_files_filepath = demultiplexed_files_filepath,
                  transfer_date = "20251027", 
                  log_dir = "test_output")

#Test with qbic barcode prefix and ncct input folder path - without demultiplexed files filepath
checkup_transfer(qportal_report_filepath = qportal_report_filepath,
                  transfer_date = "20251027", 
                  log_dir = "test_output",
                  qbic_barcode_prefix = "Q2181",
                  ncct_input_folder = "../test_data/fastq_transfer/"
                  )

#Testing with another dataset - date range
checkup_transfer(qportal_report_filepath = "../test_data/260128_NCCT_CLAVEL_QGWQH_Raw_Data_.tsv",
                  demultiplexed_files_filepath = "test_data/demultiplexed_Clavel.tsv",
                  transfer_date = "20251114-20251116", 
                  log_dir = "test_output/clavel"
                  #qbic_barcode_prefix = "QGWQH",
                  #ncct_input_folder = "test_data/fastq_transfer/"
                  )

#Testing with another dataset - date range, without demultiplexed files filepath
checkup_transfer(qportal_report_filepath = "../test_data/260128_NCCT_CLAVEL_QGWQH_Raw_Data_.tsv",
                  transfer_date = "20251114-20251116", 
                  log_dir = "test_output/clavel",
                  qbic_barcode_prefix = "QGWQH",
                  ncct_input_folder = "test_data/fastq_transfer/")


```


